IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-18 paper/formal.tex
Pass section 3
minor stuff

We are interested in proving non-interference about many programming
languages.  This requires an appropriate definition of this notion
that is language agnostic, so in this section, we present a few
general definitions for what an information flow control language is
and what non-interference properties it may have.  We also state
theorems about our system which we prove in
\appref{sec:app:proof}.
In particular, we show that |specLang alpha targetLang|, with an appropriate
scheduler |alpha|, satisfies non-interference~\cite{Goguen82},
without making any reference to properties of |targetLang|.

@@

The definition of an erasure function is quite important: it captures
the attack model, stating what can and cannot be observed by the attacker.
%
In our case, we assume that the attacker cannot observe sensitive tasks or
messages, or even the number of such entities.
%
While such assumptions are standard~\cite{Castellani:Boudol:ICALP01,
stefan:addressing-covert}, our definitions allow for
stronger attackers that may be able to inspect resource usage.\footnote{
  We believe that we can extend |specLang alpha (targetLang nop)| to
  such models using the resource limits techniques of~\cite{yangresource}.
  %
  We leave this extension to future work.
}

>>>>

We are interested in proving non-interference about many programming
languages.  This requires an appropriate definition of this notion
that is language agnostic, so in this section, we present a few
general definitions for what an information flow control language is
and what non-interference properties it may have.
In particular, we show that |specLang alpha targetLang|, with an appropriate
scheduler |alpha|, satisfies non-interference~\cite{Goguen82},
without making any reference to properties of |targetLang|.
We state the appropriate theorems here, and provide the formal
proofs in
\appref{sec:app:proof}.

@@

The definition of an erasure function is quite important: it captures
the attacker model, stating what can and cannot be observed by the attacker.
%
In our case, we assume that the attacker cannot observe sensitive tasks or
messages, or even the number of such entities.
%
While such assumptions are standard~\cite{Castellani:Boudol:ICALP01,
stefan:addressing-covert}, our definitions allow for
stronger attackers that may be able to inspect resource usage.\footnote{
  We believe that we can extend |specLang alpha (targetLang nop)| to
  such models using the resource limits techniques of~\cite{yangresource}.
  %
  We leave this extension to future work.
}
